%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage[final]{hyperref} % adds hyper links inside the
\usepackage{verbatim,color,amssymb,epsfig}
\usepackage{caption}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}

%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
% Hiring manager name
% Company
Amgen,\\
% Company Address [Street]
Thousand Oaks, CA, US.} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Se Yoon Lee Ph.D. Candidate\\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
1001 Harvey Rd Apt 68
 \\ College Station, TX 77840, U.S.A.\\(+1) (979) 888-4107% Your address and phone number
\end{center} 
\vfill

\signature{Se Yoon Lee} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Employer,} 
Please kindly accept an application from a very enthusiastic and self-motivated Ph.D. student for a Scientist-Clinical Pharmacology, Modeling and Simulation at Amgen. I am a fifth-year Ph.D. student, majoring in Statistics at Texas A\&M University. My expected graduation is on May 8th, 2021.

During my Ph.D. program, I have been explored and researched on various Bayesian statistical models, with the purpose of application towards diverse industrial problems, arising from bio-medical, health-care, oil \& gas, wind energy industries, and the COVID-19 outbreak. During the hand-on experiences, a common challenge that I have faced was the complication of the modern data structure such as enormous volume, large dimensionality, and multi-level structures. Broadly speaking, I tackle them with developing a Bayesian hierarchical model endowed with efficient computational techniques to fulfill a need of customers. 

Fortunately, I had opportunities to explore real-world problems through internships at EMD Serono and Novartis International AG. As an intern, I have collaborated with bio-medical scientists with research focuses on phase I cancer clinical trials and wet age-related macular degeneration, and relevant statistical modeling and design of experiments. Please visit following websites to see my works: \href{https://sites.google.com/view/seyoonlee/home/projects/merck-group-summer-internship-project?authuser=0}{\textcolor{gray}{$\spadesuit$Click:Work at EMD Serono $\spadesuit$}}
\href{https://sites.google.com/view/seyoonlee/home/projects/novartis-summer-internship-project?authuser=0#h.dfc3zhswkx8m}{\textcolor{brown}{$\spadesuit$ Click: Work at Novartis $\spadesuit$}}. Recently, my internship work at EMD Serono has been invited to the American Conference on Pharmacometrics 2020, one of the reputable conferences in pharmacometrics. 

% Pharma company
Now, as my graduation date gets closer day by day, my determination and passion to contribute to pharmaceutical science to serve patients and their caregivers get stronger. I truly believe that Amgen is the right place to start my career and grow. Thank you very much for your time and consideration of my application, and I am looking forward to hearing back from you. 

%Now, as my graduation date gets closer day by day, my determination and passion to contribute to the US industry get stronger. And particularly, I wish to learn and grow at the financial industry. I truly believe that Morgan Stanley is the right place to start my career and grow. Thank you very much for your time and consideration of my application, and I am looking forward to hearing back from you. 

\closing{Sincerely yours,}
\encl{Curriculum vitae} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}